FTLR proof cases

### 2018-06-26 fully-abstract-comp/ftlr-proof-cases.tex
Prove a lemma about store...

\begin{lemma}[Store to regular capability works]
  \label{lem:readcond-cap-works}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $c' = ((\perm',\lin'),\baddr',\eaddr',\aaddr')$
  \item $\perm \in \writeAllowed{}$, $\perm' \in \writeAllowed{}$
  \item $\aaddr \in [\baddr,\eaddr]$
  \item $\aaddr' \in [\baddr',\eaddr']$
  \item $\npair{(c_1,c_1')}\in\lrvg{\trusted}(H_\sigma,W)$
  \item $\npair{(c_2,c_2')}\in\lrv(H_\sigma,W)$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \item $c_3 = \linCons{c_2}$, $c_3' = \linCons{c_2'}$
  \end{itemize}
  Then $\exists W', W_M'\ldotp$
  \begin{itemize}
  \item $W_M = W' \oplus W_M'$
  \item $\memSat[n']{(\ms_S\update{\aaddr}{c_2},\stk,\ms_\stk,\ms_T\update{\aaddr'}{c_2'})}{W_M'}$
  \item $\npair[n']{(c_3,c_3')} \in \lrv(W')$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

>>>>

\begin{lemma}[Store to regular capability works]
  \label{lem:readcond-cap-works}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $c_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $c_1' = ((\perm',\lin'),\baddr',\eaddr',\aaddr')$
  \item $\perm \in \writeAllowed{}$, $\perm' \in \writeAllowed{}$
  \item $\aaddr \in [\baddr,\eaddr]$
  \item $\aaddr' \in [\baddr',\eaddr']$
  \item $\npair{(c_1,c_1')}\in\lrvg{\trusted}(H_\sigma,W_1)$
  \item $\npair{(c_2,c_2')}\in\lrv(H_\sigma,W_2)$
  \item $W_1 \oplus W_2 \oplus W_M$ is defined
  \item $n' < n$
  \item $c_3 = \linCons{c_2}$, $c_3' = \linCons{c_2'}$
  \end{itemize}
  Then $\exists W_2', W_M'\ldotp$
  \begin{itemize}
  \item $W_2 \oplus W_M = W_2' \oplus W_M'$
  \item $\memSat[n']{(\ms_S\update{\aaddr}{c_2},\stk,\ms_\stk,\ms_T\update{\aaddr'}{c_2'})}{W_M'}$
  \item $\npair[n']{(c_3,c_3')} \in \lrv(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
  From $\npair{(c_1,c_1')}\in\lrvg{\trusted}(W_1)$ and $\perm \in \writeAllowed{}$, it follows that $c_1 = c_1'$ and $\npair{[b,e]} \in \writeCond{\lin,W_1}$.

  We then get a $r$ and $A$, such that $a \in A$, $\pwheap[W_1](r).H \nsupeq \stdreg{A,\gc}{v}.H$ and $\pwheap[W_1](r)$ is address-stratified.

  If we decompose the judgement that $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$, then we get some $\npair[n-1]{\ms_S|_A, \ms_T|_A} \in \stdreg{A,\gc}{v}.H~W_{M,A}$ for some $W_M = W_{M,A} \oplus W_{M,R}$.
  If we define $W_M'$ as $W_M \oplus W_2$ and $W_2' = \purePart{W_2}$, then we can use the properties about $\pwheap[W_1](r)$ above to show that  $\memSat[n']{(\ms_S\update{\aaddr}{c_2},\stk,\ms_\stk,\ms_T\update{\aaddr'}{c_2'})}{W_M'}$.
  The fact that $\npair[n']{(c_3,c_3')} \in \lrv(W_2')$ follows from Lemma~\ref{lem:non-linear-pure}.
\end{proof}
